---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# `r emo::ji("tropical_fish")`  `r emo::ji("fish")` My Compendium `r emo::ji("fish")` `r emo::ji("tropical_fish")`    

This Compendium is full of fishes around the world `r emo::ji("earth_africa")`  `r emo::ji("earth_asia")`  `r emo::ji("tropical_fish")`.

## Authors

- François Guilhaumon

## Contact

francois.guilhaumon@ird.fr

## Script list

```{r}
list.files(file.path("R"))
```



## Session info

```{r}
sessionInfo()
```

## Sources url

Cruise track:

    1-second resolution: https://doi.org/10.5281/zenodo.3260616
    1-minute resolution: https://doi.org/10.5281/zenodo.3483166
    1-hour resolution: https://doi.org/10.5281/zenodo.3483164

Meteorology data: https://doi.org/10.5281/zenodo.3379590

CTD data: https://doi.org/10.5281/zenodo.3247384

Many projects have now published datasets as well. 
Those that were published through SPI can be found here: https://zenodo.org/communities/spi-ace/search?page=1&size=20



Published data

    You are here:Home Published data

Datasets

All data published from ACE can be found here. More data will be available over the coming months.

Other datasets have already been published elsewhere:
Dataset name 	Link / DOI
Acoustic recordings of whales from Sonobuoys 	doi:10.4225/15/59d5a05f6050f
Reconstructed non-linear surface from WAMOS (marine radar) 	doi:10.26179/5b8378b160b02
Unidirectional wave spectra from WaMoS (marine radar) 	doi:10.4225/15/5a17923429cb7
Aerosol optical density 	https://aeronet.gsfc.nasa.gov/new_web/cruises_new/Ak_Treshnikov_16_17.html
SOCCOM / Bio-ARGO float 	http://www.argodatamgt.org/Access-to-data/Argo-data-selection, platform codes: 5905069, 5905070, 5905072, 5905073
Benthic and intertidal organism specimens 	http://www.ozcam.org.au/
Seabird and marine mammal observations 	http://seabirds.saeon.ac.za/
Antarctic springtail occurrence records 	10.26180/5cd37a14de28b

Data publications

``Leihy, R. I., Duffy, G. A., Nortje, E., & Chown, S. L. (2018). High resolution temperature data for ecological research and management on the Southern Ocean Islands. Scientific Data, 5, 180177.

Landwehr, S., Thurnherr, I., Cassar, N., Gysel-Beer, M., and Schmale, J.: Using global reanalysis data to quantify and correct airflow distortion bias in shipborne wind speed measurements, Atmos. Meas. Tech. Discuss. in review, 2019.


- Source chlorophyll data (8-day temporal resolution) - Ocean color 
https://oceandata.sci.gsfc.nasa.gov/MODIS-Aqua/Mapped/8-Day/4km/chlor_a/2017/